Descriptives and model description

### 2022-12-08 descriptives.qmd
add plots for missingness

### packages
library(tidyverse)
library(stringi)
library(gt)
library(ggplot2)

@@

```{r}
# plot hierarchies and covariates

# Calculate the proportions of children and girls/women
dem_longMissing <- dem_longMissing %>%
  mutate(children = rowSums(select(., female_0_4, female_5_11, female_12_17,
                            male_0_4, male_5_11, male_12_17)),
         childrenProp = children/total,
         femaleProp = female/total,
         )

@@

p.children.gni <- ggplot(data = dem_longMissing %>% 
                       filter(origin_iso3 %in% top_origin_iso3$origin_iso3, missing == "none"),
       aes(x = gni_diff, y = childrenProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country) + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

p.female.gni <- ggplot(data = dem_longMissing %>% 
                       filter(origin_iso3 %in% top_origin_iso3$origin_iso3, missing == "none"),
       aes(x = gni_diff, y = femaleProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country) + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

p.children.dist <- ggplot(data = dem_longMissing %>% 
                       filter(origin_iso3 %in% top_origin_iso3$origin_iso3, missing == "none"),
       aes(x = distance, y = childrenProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country) + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

p.female.dist <- ggplot(data = dem_longMissing %>% 
                       filter(origin_iso3 %in% top_origin_iso3$origin_iso3, missing == "none"),
       aes(x = distance, y = femaleProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country) + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

>>>>

### packages
library(tidyverse)
library(stringi)
library(gt)
library(ggplot2)
library(patchwork)

@@

```{r}
##### II. Plot hierarchies and covariates #####

# Calculate the proportions of children and girls/women
dem_longMissing <- dem_longMissing %>%
  mutate(children = rowSums(select(., female_0_4, female_5_11, female_12_17,
                            male_0_4, male_5_11, male_12_17)),
         adults = rowSums(select(., female_18_59, female_60,
                            male_18_59, male_60)),
         childrenProp = children/total,
         femaleProp = female/total,
         missingAge = case_when(
              missing == "none" ~ "Age not missing",
              missing != "none" ~ "Age missing" 
            )
         )

### plot covariates against proportions of children and female

@@

dem_longMissing_plots <- dem_longMissing %>% 
  filter(origin_iso3 %in% top_origin_iso3$origin_iso3, missing == "none", total >=50)

p.children.gni <- ggplot(data = dem_longMissing_plots,
       aes(x = gni_diff, y = childrenProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country) + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

p.female.gni <- ggplot(data = dem_longMissing_plots,
       aes(x = gni_diff, y = femaleProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country) + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

p.children.dist <- ggplot(data = dem_longMissing_plots,
       aes(x = distance, y = childrenProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country) + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

p.female.dist <- ggplot(data = dem_longMissing_plots,
       aes(x = distance, y = femaleProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country) + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

### plot missingness

# by origin region
t.oriregion.missingAge <- dem_longMissing %>% 
  group_by(missingAge,  origin_region) %>% 
  summarise(total = sum(total),
            children = sum(children),
            adults = sum(adults))

p.oriregion.missingAge1 <- ggplot(data = t.oriregion.missingAge %>%
                                   filter(origin_region!="Oceania", missingAge == "Age not missing") %>% 
                                    pivot_longer(cols = c(children, adults), names_to = "age", values_to = "value"),
                                                 aes(x = origin_region, 
                                                     y = value, 
                                                     fill = age)) +
  geom_bar(stat="identity") +
  scale_fill_manual(values=c(unhcrPaletteBlue[1], unhcrPaletteGreen[1])) +
  ggtitle("Age data available") +
  ylim(c(NA,5000000)) +
  theme(legend.position = "bottom") +
  theme_minimal()

p.oriregion.missingAge2 <- ggplot(data = t.oriregion.missingAge %>%
                                   filter(origin_region!="Oceania", missingAge == "Age missing") ,
                                                 aes(x = origin_region, 
                                                     y = total)) +
  geom_bar(stat = "identity", colour = unhcrPaletteBlue[1], fill = unhcrPaletteWhite[1], alpha = 0)  +
  ggtitle("Age data missing") +
  theme_minimal()

p.oriregion.missingAge1  + p.oriregion.missingAge2+ plot_layout(guides = "collect") & theme(legend.position = "bottom") & ylim(c(NA,11000000))

# by asylum region
t.asyregion.missingAge <- dem_longMissing %>% 
  group_by(missingAge,  asylum_region) %>% 
  summarise(total = sum(total)) %>% 
  mutate(totalProp = total/sum(total))

p.asyregion.missingAge <- ggplot(data = t.asyregion.missingAge,
                                                 aes(x = asylum_region, 
                                                     y = totalProp*100)) +
  geom_bar( stat="identity", fill = unhcrPaletteBlue[1]) +
  facet_wrap(~  missingAge,  scales = "fixed")
